---
title: "R Notebook"
output: html_notebook
---
All code and examples are from https://sites.google.com/site/doingbayesiandataanalysis/

```{r, setup}
knitr::opts_knit$set(root.dir = normalizePath(".")) 
```


# Chapter 02: Introduction

## 2.3.3 A Simple Example of R in Action

```{r}
source("DBDA2Eprograms/SimpleGraph.R")
```

## Exerises

### 2.5 see above

### 2.6
```{r}
x <- seq(from = -3, to = 3, by = 0.1)
y <- x^3
plot(x, y, type = "l")
```

# Chapter 03: Stuff Called Probability

## 3.2.1.1 Simulating a Long-Run Relative Frequence

### 3.5.1

The goal is to toss a coin N times and compute the running proporiton of heads.

```{r}
source("DBDA2Eprograms/RunningProportion.R")
```

### 3.5.2

```{r}
source("DBDA2Eprograms/IntegralOfDensity.R")
```


# Chapter 06: Binomial Probability (in 2nd edition)
## Chapter 05 in first edition

```{r}
source("DBDA2Eprograms/BernBetaExample.R")
```

### 5.6: Exercises (first edition)

```{r}
# 5.1

post <- BernBeta( priorBetaAB = c(4, 4), Data = c(1), plotType = "Bars", 
                 showCentTend = "Mode", showHDI = TRUE, showpD = FALSE )
# get heads again
post <- BernBeta( priorBetaAB = post, Data = c(1) )
# get tails
post <- BernBeta( priorBetaAB = post, Data = c(0) )



## same updating using sequence THH instead of HHT
post <- BernBeta( priorBetaAB = c(4,4), Data = c(0) )
# get heads again
post <- BernBeta( priorBetaAB = post, Data = c(1) )
# get tails
post <- BernBeta( priorBetaAB = post, Data = c(1) )



# 5.2
post <- BernBeta( priorBetaAB = c(1,1), Data = c(rep(1, 58), rep(0, 42)),
                  showCentTend = "Mean", showHDI = TRUE, showpD = FALSE)

## HDI: (0.483, 0.673)
## Yes, it is credible to believe the population is equally divided
post <- BernBeta( priorBetaAB = c(58,42), Data = c(rep(1, 57), rep(0, 43)),
                  showCentTend = "Mean", showHDI = TRUE, showpD = FALSE)

# HDI: (0.507, 0.643)
# No, it is not credible now because the HDI does not contain .5


## 5.3
post_radio <- BernBeta( priorBetaAB = c(1, 1), Data = c(rep(1, 40), rep(0, 10)),
                  showCentTend = "Mean", showHDI = TRUE, showpD = FALSE)
# HDI: (0.677, 0.893)

post_ocean <- BernBeta( priorBetaAB = c(1, 1), Data = c(rep(1, 15), rep(0, 35)),
                  showCentTend = "Mean", showHDI = TRUE, showpD = FALSE)
# HDI: (0.187, 0.433)


## 5.4
post <- BernBeta( priorBetaAB = c(0.5, 0.5), Data = c(rep(1, 4), rep(0, 1)),
                  showCentTend = "Mean", showHDI = TRUE, showpD = FALSE)
# [1] 4.5 1.5


## 5.6

post1 <- BernBeta( priorBetaAB = c(1, 1), Data = c(rep(1, 15), rep(0, 5)),
                  showCentTend = "Mean", showHDI = TRUE, showpD = FALSE)
post2 <- BernBeta( priorBetaAB = c(10, 10), Data = c(rep(1, 15), rep(0, 5)),
                  showCentTend = "Mean", showHDI = TRUE, showpD = FALSE)

(post1[1]/sum(post1))/(post2[1]/sum(post2))

```

## Chapter 06 in first edition

```{r}
source("DBDA2Eprograms/BernGridExample.R")
```

### 6.8: Exercises (first edition)

```{r}
## 6.1

nIntervals <- 10
width <- 1/ nIntervals
Theta <- seq(from = width/2, to = 1 - width/2, by = width)
approxMass <- dbeta(Theta, 8, 4) * width
pTheta <- approxMass / sum(approxMass)

sum(approxMass)

## 6.2
pTheta <- c(50:1, rep(1, 50), 1:50, 50:1)
pTheta <- pTheta / sum(pTheta)
width <- 1 / length(pTheta)
Theta <- seq(from = width/2, to = 1 - width/2, by = width)

BernGrid( Theta = Theta, pTheta = pTheta, Data = c(rep(1, 15),rep(0, 5)),
          plotType = "Bars", showCentTend = "Mean",
                     showHDI = TRUE, HDImass=0.95 ,
                     showpD = TRUE, nToPlot=min(2001,length(Theta)) )
# HDI: (0.602, 0.878)

## 6.3
postA <- BernGrid( Theta = Theta, pTheta = pTheta, Data = c(rep(1, 3),rep(0, 1)),
          plotType = "Bars", showCentTend = "Mean",
                     showHDI = TRUE, HDImass=0.95 ,
                     showpD = TRUE, nToPlot=min(2001,length(Theta)) )

postB <- BernGrid( Theta = Theta, pTheta = postA, Data = c(rep(1, 15),rep(0, 5)),
          plotType = "Bars", showCentTend = "Mean",
                     showHDI = TRUE, HDImass=0.95 ,
                     showpD = TRUE, nToPlot=min(2001,length(Theta)) )

## 6.6
binwidth <- 1/1000
thetagrid <- seq( from = binwidth/2, to = 1 - binwidth/2, by = binwidth )
relprob <- thetagrid ^ 2
prior <- relprob / sum(relprob) # probabilit mass at each theta
  
posterior <- BernGrid( Theta = thetagrid, pTheta = prior, 
                       Data = c(rep(1, 2),rep(0, 2)),
                       plotType = "Bars", showCentTend = "Mean",
                       showHDI = TRUE, HDImass=0.95 ,
                       showpD = TRUE, nToPlot=min(2001,length(Theta)) )
sum( thetagrid * posterior )


## 6.7
binwidth <- 1/1000
thetagrid <- seq( from = binwidth/2, to = 1 - binwidth/2, by = binwidth )
relprob <- thetagrid ^ 2
prior <- relprob / sum(relprob) # probabilit mass at each theta

posteriorM1 <- BernGrid( Theta = thetagrid, pTheta = prior, 
                       Data = c(rep(1, 6),rep(0, 2)),
                       plotType = "Bars", showCentTend = "Mean",
                       showHDI = TRUE, HDImass=0.95 ,
                       showpD = TRUE, nToPlot=min(2001,length(Theta)) )
M1post_mean <- sum( thetagrid * posteriorM1 )


binwidth <- 1/1000
thetagrid <- seq( from = binwidth/2, to = 1 - binwidth/2, by = binwidth )
relprob <- (1 - thetagrid) ^ 2
prior <- relprob / sum(relprob) # probabilit mass at each theta

posteriorM2 <- BernGrid( Theta = thetagrid, pTheta = prior, 
                       Data = c(rep(1, 6),rep(0, 2)),
                       plotType = "Bars", showCentTend = "Mean",
                       showHDI = TRUE, HDImass=0.95 ,
                       showpD = TRUE, nToPlot=min(2001,length(Theta)) )
M2post_mean <- sum( thetagrid * posteriorM2 )

M1post_mean / M2post_mean
```




# Chapter 07: Markov Chain Monte Carlo

## Exercises 7.2

```{r}

## 7.7
proposalSD <- c(0.02, 0.2, 2.0)[3]

source("DBDA2Eprograms/BernMetrop.R")

## 7.2
openGraph(height = 7, width = 3.5) # open blank graph window
layout(matrix(1:2, nrow = 2)) # creates a 2 by 1 layout for the plots
acf( acceptedTraj, lag.max = 30, col = "skyblue", lwd = 3 ) # creates acf plot and places on top plot
Len <- length( acceptedTraj ) # length of the chain
Lag <- 10 # lag number to observe
trajHead <- acceptedTraj[1 : (Len - Lag)] # accept trajectory for heads
trajTail <- acceptedTraj[(1 + Lag) : Len] # accept trajectory for tails
plot( trajHead, trajTail, pch = ".", col = "skyblue",
      main = bquote( list("Prpsl.SD" == .(proposalSD),
                          lag == .(Lag),
                          cor == .(round(cor(trajHead, trajTail), 3)))))  # creates scatter plot


## 7.3

theta <- seq(0, 1, length = 501)
ptheta <- (cos(4*pi*theta) + 1)^2/1.5
plot(theta, (cos(4*pi*theta) + 1)^2/1.5)

source("DBDA2Eprograms/BernMetrop.R")

```


# Chapter 08: JAGS


## 8.4: Example: Difference of Biases
```{r}
source("DBDA2Eprograms/Jags-Ydich-XnomSsubj-MbernBeta.R")

myData <- read.csv("DBDA2Eprograms/z6N8z2N7.csv")
y <- myData$y
s <- myData$s
Ntotal <- length(y)
Nsubj <- length(unique(s))
dataList <- list(
  y = y,
  s = s,
  Ntotal = Ntotal,
  Nsubj = Nsubj
)

codaSamples <- genMCMC(data = myData, numSavedSteps=50000 , saveName=NULL )

smryMCMC( codaSamples = codaSamples, compVal = 0.5, rope = NULL, compValDiff = 0.0, ropeDiff = NULL, saveName = NULL )

plotMCMC( codaSamples = codaSamples, data = myData, compVal = 0.5, rope=NULL,
          compValDiff = 0.0, ropeDiff = NULL, saveName = "XnomSsubj-MbernBeta", saveType = "png" )
```






# Chapter 13

```{r}
source("DBDA2Eprograms/minNforHDIpower-example.R")
```




