---
title: "R Notebook"
output: html_notebook
---
All code and examples are from https://sites.google.com/site/doingbayesiandataanalysis/

```{r, setup}
knitr::opts_knit$set(root.dir = normalizePath(".")) 
```


# Chapter 02: Introduction

## 2.3.3 A Simple Example of R in Action

```{r}
source("DBDA2Eprograms/SimpleGraph.R")
```

## Exerises

### 2.5 see above

### 2.6
```{r}
x <- seq(from = -3, to = 3, by = 0.1)
y <- x^3
plot(x, y, type = "l")
```

# Chapter 03: Stuff Called Probability

## 3.2.1.1 Simulating a Long-Run Relative Frequence

### 3.5.1

The goal is to toss a coin N times and compute the running proporiton of heads.

```{r}
source("DBDA2Eprograms/RunningProportion.R")
```

### 3.5.2

```{r}
source("DBDA2Eprograms/IntegralOfDensity.R")
```


# Chapter 06: Binomial Probability (in 2nd edition)
## Chapter 05 in first edition

```{r}
source("DBDA2Eprograms/BernBetaExample.R")
```

### 5.6: Exercises (first edition)

```{r}
# 5.1

post = BernBeta( priorBetaAB = c(4, 4), Data = c(1), plotType = "Bars", 
                 showCentTend = "Mode", showHDI = TRUE, showpD = FALSE )
# get heads again
post <- BernBeta( priorBetaAB = post, Data = c(1) )
# get tails
post <- BernBeta( priorBetaAB = post, Data = c(0) )



## same updating using sequence THH instead of HHT
post = BernBeta( priorBetaAB = c(4,4), Data = c(0) )
# get heads again
post <- BernBeta( priorBetaAB = post, Data = c(1) )
# get tails
post <- BernBeta( priorBetaAB = post, Data = c(1) )

# 5.2


```

## Chapter 06 in first edition

```{r}
source("DBDA2Eprograms/BernGridExample.R")
```

### 6.8: Exercises (first edition)

```{r}

```




# Chapter 7: Markov Chain Monte Carlo






# Chapter 13

```{r}
source("DBDA2Eprograms/minNforHDIpower-example.R")
```




